A Switching Planner for Combined Task and Observation Planning

### 2010-11-19 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Want to remove missleading text I had in the introduction.
 - Charles

We developed a first-order declarative language, called DTPDDL, for
describing domains of planning problems that correspond to POMDPs.  To
accompany that language we have implemented an information-state
\laostar\ procedure for solving problems expressed in DTPDDL. We have
an automated determinisation procedure that generates MAPL
descriptions given DTPDDL input. To accompany that, we have extended
MAPSIM to simulate DTPDDL instances, and modified \fastdownward\ so
that it can find useful serial executions given DTPDDL and MAPL models
of the problem at hand.

>>>>

We developed a first-order declarative language, called DTPDDL, for
describing domains of planning problems that correspond to POMDPs.  To
accompany that language we have implemented an information-state
\laostar\ procedure for solving problems expressed in DTPDDL.

We have extended MAPSIM to simulate DTPDDL instances, and modified
\fastdownward\ so that it can find useful serial executions given
DTPDDL models of the problem at hand.
